A sustainable approach to tourist signage on heritage trails\footnote{This research has been supported by the Ministry of University and Research under the "Underlandscape" project (2020428LS8)}

### 2023-11-07 paper.tex
Integra modifiche durante la call 6/11, modifiche di Letizia e di Maria Grazia

Casoli village boasts a heterogeneous range of tourist attractions, including both soft and hard outdoor experiential activities, such as: canyoning, rafting, and trekking experiences in the Canyon park. Additionally, it features Romanesque churches and huts attracting visitors looking for various experiences such as thermal, environmental, outdoor, sport and cultural activities. Throughout the year, local stakeholders offer a variety of services, often incorporating sustainable tourism practices. After a detailed analysis of the tourist and social context of Bagni di Lucca, it can be claimed that the area boasts a good tourist appeal towards Italian and foreign tourists searching for various kinds of touristic experiences \cite{x} dating back to the ‘90s, when some associations began organizing mainly trekking excursions and rafting experiences (\citeWeb{agu,r2o,ronda,garfraft,valdilima,canyonpark,experience,ebikea,ebikel,bdlt2,bdl}).

As part of Bagni di Lucca's ecosystem, with its focus on tourism, Casoli is a destination for slow travel. It is important to ensure that any development actions taken are sustainable, in order to preserve its unique social fabric. This means paying attention to conservation of the environment and cultural heritage, as well as preserving intergenerational continuity and economic equity \cite{x}.

@@

>>>>

Casoli village boasts a heterogeneous range of tourist attractions, including both soft and hard outdoor experiential activities, such as: canyoning, rafting, and trekking experiences in the Canyon park. Additionally, it features Romanesque churches and huts attracting visitors looking for various experiences such as thermal, environmental, outdoor, sport and cultural activities. Throughout the year, local stakeholders offer a variety of services, often incorporating sustainable tourism practices. After a detailed analysis of the tourist and social context of Bagni di Lucca, it can be claimed that the area boasts a good tourist appeal towards Italian and foreign tourists searching for various kinds of touristic experiences \cite{loz09} dating back to the ‘90s, when some associations \citeWeb{agu,r2o,ronda,garfraft,valdilima,canyonpark,experience,ebikea,ebikel,bdlt2,bdl} began organizing mainly trekking excursions and rafting experiences .

As part of Bagni di Lucca's ecosystem, with its focus on tourism, Casoli is a destination for slow travel. It is important to ensure that any development actions taken are sustainable, in order to preserve its unique social fabric. This means paying attention to conservation of the environment and cultural heritage, as well as preserving intergenerational continuity and economic equity \cite{kuh10a}.

@@

Based on qualitative and quantitative analysis \cite{loz09} carried out in the social and touristic context of Bagni di Lucca, including the Casoli village, it can be argued that the area under investigation has unique features that need to be capitalized on to enhance its tourism potential. Given the touristic trends and the local vocation, we conclude that Casoli is a small destination for potential tourists practicing heterogeneous touristic circuits in individual and combined ways. Our study aims to involve stakeholders in sustainable planning for new heritage itineraries, despite accessibility limitations on site.
